Bayesian exponential random graph modeling of KWL Burial network

### 2020-10-03 analysis/paper/paper.Rmd
edit Intro

<!--burial study- network analysis-->
Burials provide valuable information about social structures that can reflect not only the personal life and status of the deceased, but also the expressions of their descendants through grave goods [@Pearson1999]. This enables the study of social differences based on burials to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. Mortuary practices such as burial forms, grave goods, and related ritual practices could represent the social relations between individuals and allow us to infer social structures, for examples, grave goods usually relate to social practices of trade, exchange, and gifting [@Coward2013, pp. 252]. One way to study the relationships between individual is social network analysis (SNA), which can visualize, quantify, and statistically test hypotheses about the relationships to understand network structure and its effects on every part within the network [@Freeman2004; @Salvini2010]. A social network contains a set of actors and a set of relationships connecting these actors, which could be groups, organizations or persons. Their relationships are flows of resources that reflect relations of control, dependence, and cooperation. In other words, actors are viewed as "nodes" in a wider network, in which nodes are connected by multiple relationships, or "edges", to other nodes [@Coward2013; @Mizoguchi2013; @Potgieter2008].

>>>>

<!--burial study- network analysis-->
Burials provide valuable information about past human behavior that can reflect not only the personal life and status of the deceased, but also the expressions of their descendants through grave goods and arrangements [@Pearson1999]. Mortuary practices such as burial forms, grave goods, and related ritual practices could represent the social relations between individuals and allow archaeologists to infer social structures. This enables the study of social differences based on burials to answer questions related to social inequality and complexity [@Ehrhardt2009; @Gamble2002; @Janes2013; @Johansen2015]. For examples, grave goods can reflect consumption patterns and social practices in a broader of cultural contexts involves personal identity or social relation through trade, exchange, and gifting [@Coward2013, pp. 252]. The correlation between burials could be viewed as an indicator of social relationship in a society. One way to study the relationships between individual is social network analysis (SNA). A social network contains a set of actors and a set of relationships connecting these actors, which could be groups, organizations or persons. SNA can quantify, visualize, and statistically test hypotheses of the relationships between actors to examine the structure of network and major factors that affect the structure of the network [@Freeman2004; @Salvini2010]. To be specific, actors are "nodes" in a wider network, in which nodes are connected by multiple relationships, or "edges", to other nodes [@Coward2013; @Mizoguchi2013; @Potgieter2008]. Relationships can be viewed as flows of resources that reflect relations of control, dependence, and cooperation, reflecting social relation in a given society.
